Why is it that statistical tests for residuals are not widely used? An explanation using visual inference.

### 2023-03-03 paper_comparison/paper_comparison/paper_comparison.Rmd
add hypotheses discussion

## Hypotheses

A paragraph on what hypothesis(es) are being tested.

Generally, by looking at the residuals we are concerned with

$H_o:$ The model specification is correct

against a broad alternative that something is missing:

$H_a:$ The model specification is not correct

The conventional tests are only equipped to measure specific departures, and thus have a more specific hypotheses being tested:

XXX

>>>>

## hypotheses

Before the discussion of the p-value and power, the difference in hypotheses between conventional tests and visual tests worth a clarification.

Generally, by examining the residuals we are concerned with

$$H_0: \text{The regression model is correctly specified}$$

against a broad alternative hypothesis that

$$H_1: \text{The regression model is misspecified.}$$

The conventional tests are only equipped to measure specific residual departures, and thus have a more specific null and alternative hypotheses being tested. For instance, the RESET test with the auxiliary regression formulated as $$\boldsymbol{e} = \gamma_1\hat{\boldsymbol{y}}^2 + \gamma_2\hat{\boldsymbol{y}}^3 + \gamma_3\hat{\boldsymbol{y}}^4 + \boldsymbol{u}, \boldsymbol{u} \sim N(\boldsymbol{0}, \sigma_u^2\boldsymbol{I})$$ has $H_0:\gamma_1 = \gamma_2 = \gamma_3 = 0$ and $H_1: \gamma_1 \neq 0 \text{ or } \gamma_2 \neq 0 \text{ or } \gamma_3 \neq 0$. In contrast, the visual test has the null hypothesis same as the general $H_0$ and $H_1$ provided above. Essentially, a visual test can be seen as a collection of tests targeting for different residual departures.

### 2023-03-03 paper_comparison/paper_comparison/paper_comparison.tex
add hypotheses discussion

\hypertarget{hypotheses}{%
\subsection{Hypotheses}\label{hypotheses}}

A paragraph on what hypothesis(es) are being tested.

Generally, by looking at the residuals we are concerned with

\(H_o:\) The model specification is correct

against a broad alternative that something is missing:

\(H_a:\) The model specification is not correct

The conventional tests are only equipped to measure specific departures,
and thus have a more specific hypotheses being tested:

XXX

>>>>

\hypertarget{hypotheses}{%
\subsection{hypotheses}\label{hypotheses}}

Before the discussion of the p-value and power, the difference in
hypotheses between conventional tests and visual tests worth a
clarification.

Generally, by examining the residuals we are concerned with

\[H_0: \text{The regression model is correctly specified}\]

against a broad alternative hypothesis that

\[H_1: \text{The regression model is misspecified.}\]

The conventional tests are only equipped to measure specific residual
departures, and thus have a more specific null and alternative
hypotheses being tested. For instance, the RESET test with the auxiliary
regression formulated as
\[\boldsymbol{e} = \gamma_1\hat{\boldsymbol{y}}^2 + \gamma_2\hat{\boldsymbol{y}}^3 + \gamma_3\hat{\boldsymbol{y}}^4 + \boldsymbol{u}, \boldsymbol{u} \sim N(\boldsymbol{0}, \sigma_u^2\boldsymbol{I})\]
has \(H_0:\gamma_1 = \gamma_2 = \gamma_3 = 0\) and
\(H_1: \gamma_1 \neq 0 \text{ or } \gamma_2 \neq 0 \text{ or } \gamma_3 \neq 0\).
In contrast, the visual test has the null hypothesis same as the general
\(H_0\) and \(H_1\) provided above. Essentially, a visual test can be
seen as a collection of tests targeting for different residual
departures.
